Innovations Report: Procedural Fur System

### 2018-03-16 docs/paper.tex
more on docs

>>>>

There are many different methods one could use to distribute points on an abritrary mesh, however for replicating creature fur it is desirable to choose a method that distributes primitives at random positions across the surface, yet roughly evenly spaced from neighboring primitives. A popular method used to achieve this kind of distribution is referred to as 'Dart Throwing', which relies on checking the distance to neighboring samples after a new sample has been generated, and discarding the sample if the samples are too close. Whilst these kinds of methods produce good results, they can be inefficient as in certain situations many samples may be generated and rejected, before a sample is accepted. An optimisation for this is described in \textit{Dart Throwing on Surfaces} \cite{dartThrowing}, which relies on removing areas of the mesh that are already covered by a sample, by means of triangle subdivision.

Unfortunately, parallelizing dart thowing methods is not trivial, making them unsuitable for my desired usage of OpenGL compute shaders. Whilst sampling methods suitable for parallel processing do exist, such as those described in \textit{Parallel Poisson Disk Sampling with Spectrum Analysis on Surfaces} \cite{parallelPoisson}, I instead opted to implement a naive random samling method as it was much easier to parallelize.

\begin{enumerate}
\item Generate a uniform random number in the range [0.0 - 1.0].
\end{enumerate}
